Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-12-02 analysis/paper/paper.Rmd
updated CPUE to also include a metric of fish / angler day, and large fish (>= 228mm) / angler day, to compare with other reports.

```{r spring-abund}
total_cpue = cpue_df %>%
              mutate(across(event_name,
                            ~ str_replace(., "_", " "))) %>%
              group_by(species, event_name) %>%
              summarise(across(c(total_effort, n_fish),
                               sum),
                        .groups = "drop") %>%
              mutate(across(total_effort,
                            ~ . / 60)) %>%
              mutate(cpue = n_fish / total_effort)

@@

```{r cpue-fig, fig.cap = "Total catch per unit effort across entire sampling event."}
cpue_df %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  group_by(species, event_name) %>%
  summarise(across(c(total_effort, n_fish),
                   sum),
            .groups = "drop") %>%
  mutate(across(total_effort,
                ~ . / 60)) %>%
  mutate(cpue = n_fish / total_effort) %>%
  ggplot(aes(x = event_name,
             y = cpue,
             fill = event_name)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1",
                    name = "Event") +
  labs(x = "Event",
       y = "CPUE (Pikeminnow caught per hour)") +
  theme(legend.position = "none")

>>>>

```{r spring-abund}
total_cpue = cpue_df %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  group_by(species, event_name) %>%
  summarise(across(c(total_effort, 
                     n_fish,
                     n_large_fish,
                     angler_days = crew_count),
                   sum),
            .groups = "drop") %>%
  mutate(across(total_effort,
                ~ . / 60)) %>%
  mutate(cpue = n_fish / total_effort,
         cpue_per_day = n_fish / angler_days,
         cpue_large_per_day = n_large_fish / angler_days)

@@

```{r cpue-fig, fig.cap = "Total catch per unit effort across entire sampling event."}
total_cpue %>%
  ggplot(aes(x = event_name,
             y = cpue_large_per_day,
             fill = event_name)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1",
                    name = "Event") +
  labs(x = "Event",
       y = "CPUE (Large Pikeminnow caught per angler day)") +
  theme(legend.position = "none")
